
---
title: "HTGQC Vignette"
author: "Lodovico Terzi di Bergamo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HTGQC vignette

This is the vignette for the HTGQC package for the quality control of HTG EDGE-Seq protocols.
Please visit <https://github.com/LodovicoTerzi/HTGQC> for more details.

Please install and load this list of dependencies:

```{install dependencies}
library(readxl)
library(ggplot2)
library(edgeR)
library(assertthat)
library(knitr)
```

If the input file is the unformatted Excel file, it can be read using the readHTG function as follows:

```{readHTG}
path.unformatted <- "/path/to/excel/file"
dat.formatted <- readHTG(dat.unformatted)
head(dat.formatted)
```

Otherwise, please load the pre-formatted file with gene names as row names

```{readHTG}
library(dplyr)
path.formatted <- "/path/to/preformatted/file"
dat.formatted <- read_excel(dat.unformatted) %>% as.data.frame() %>% column_to_rownames("GeneID")
head(dat.formatted)
```

Now you can run the quality control as follows

```{qualityControl}
qualityCheck(dat.formatted)
```

\
\
\
Below is an example of the Negative Controls plot. \
The green and red line represent the 2\*standard deviation and 3\*standard deviation range. \

![NegPlot](/Users/lodovico/Desktop/IOR/HTG_QC/QC/NegativePlot.svg){width=100%}



\
\
\
Similarly, below is an example of the Positive Controls plot. \
The red line indicates ther threshold for the FAIL filter, set at 40%. \

![PosPlot](/Users/lodovico/Desktop/IOR/HTG_QC/QC/PositivePlot.svg){width=100%}

\
\
\
Finally, below is an example of the Positive Controls table, wthe the "QC_result" variable indicating for each sample if the quality control was OK, ALERT, or FAIL. \

```{r echo =TRUE}
tab <- read.csv("https://raw.githubusercontent.com/LodovicoTerzi/HTGQC/main/dataExample/QC/PositiveTable.csv")  %>% column_to_rownames("sample_names")
knitr::kable(head(tab))
```









